Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-08-22 analysis/paper/paper-doc.qmd
review 'basic-analysis' and delete code we don't use
minor edits around fig 3

@@

![Boxplot for each attribute measured on the stemmed points. The black bold horizontal lines in the middle of boxes represent the median value.](images/002-attributes-variation-01.png){#fig-three width="324"}

>>>>

```{r}

```

@@

![Boxplot for each attribute measured on the stemmed points. The black bold horizontal lines in the middle of boxes represent the median value. The dots represent individual artefacts.](images/002-attributes-variation-01.png){#fig-three width="324"}
